SPEI by stations

### 2017-11-08 analysis/drought/explore_drought_station.Rmd
add map

---
title: "SPEI by stations"
author: "AJ Perez-Luque (@ajpelu)"
date: "2016 Sep"
output:  
  md_document:
    toc: true
    variant: markdown_github
---

@@

```{r, eval=FALSE}
# Map of station

>>>>

---
title: "SPEI by stations"
author: "AJ Perez-Luque (@ajpelu)"
date: "2016 Sep"
output:  
  md_document:
    toc: true
    variant: markdown_github
always_allow_html: yes
---

@@

```{r}
# Map of station
